\Title

### 2016-03-22 manuscript/manuscript.tex
Make subsection for hyper-param estimation
The two other two subsections are subsubsections and add an opening
paragraph for overview.

Fixes #21

\subsubsection{The regularization parameter}

@@

\noindent
in which $N_{test}$ is the number of data in the testing set.
The optimal value of $\mu$ will be the one that minimizes the MSE,
i.e. the one that best predicts the testing data.
We emphasize that the inversion is performed only on the training data set.

@@

The separation of the training and testing data sets is commonly done by taking
random samples from the full data set.
However, we cannot perform the separation in this way because
Bott's method requires data on a regular grid as well as having model elements
directly below each data point.
Thus, we take as our training set the points from the observed data grid that
fall on a similar grid but with twice the grid spacing
(white dots with black outlines in Fig.~\ref{fig:grid_separation}).
All other points from the original data grid
make up the testing data set
(black dots in Fig.~\ref{fig:grid_separation}).
This separation will lead to
a testing data set with more points than the training data set.
A way to balance this loss of data in the inversion
is to generate a data grid with half of the desired grid spacing,
either through interpolation
or from a spherical harmonic model.

\subsubsection{$z_{ref}$ and $\Delta\rho$}

@@

We perform the cross-validation procedures in two parts.
First, we run the cross-validation to estimate
an optimal regularization parameter ($\mu$).
The starting estimate for all inversions is
60 km depth for all model parameters.
For this cross-validation,
we keep $z_{ref}$ and $\Delta\rho$ fixed to
$20\ km$ and $500\ kg/m^3$, respectively.
Our investigations suggest that the outcome of this round of cross-validation
does not depend on the particular values of $z_{ref}$ and $\Delta\rho$ used.
Second, we use the estimated $\mu$ to run the cross-validation
to estimate $z_{ref}$ and $\Delta\rho$,
thus obtaining the final estimated Moho depths.
Fig.~\ref{fig:crust1-results} summarizes the results
from both cross-validation runs and the final inversion results.

>>>>

Parameters that influence the inversion result but are not estimated directly
in the inversion are known as hyper-parameters.
In the case of our regularized Moho depth inversion, the hyper-parameters are
the regularization parameter $\mu$ (Eq.~\ref{eq:goalfunction}),
the Moho density-contrast $\Delta \rho$ (Eq.~\ref{eq:bott-gaussnewton}),
and the depth of the Normal Earth Moho, or reference level, $z_{ref}$
(Fig.~\ref{fig:anomalysketch}b).

We estimate these hyper-parameters in two steps.
First, we assume fixed values for
$z_{ref}$ and $\Delta\rho$ and perform a cross-validation procedure
\citep{hansen1992} to estimate an optimal value for $\mu$.
Our investigations suggest that the outcome of this round of cross-validation
does not depend on the particular values of $z_{ref}$ and $\Delta\rho$ used.
Second, we use the estimated $\mu$ to perform a second cross-validation
procedure to estimate $z_{ref}$ and $\Delta\rho$.
The outcome of both cross-validations is not only the values of the three
hyper-parameters but the final estimated Moho depths.

\subsubsection{Estimating the regularization parameter}

@@

\noindent
in which $N_{test}$ is the number of data in the testing set.
The optimal value of $\mu$ will be the one that minimizes the MSE,
i.e. the one that best predicts the testing data.
We emphasize that the inversion is performed on the training data set only.

@@

The separation of the training and testing data sets is commonly done by taking
random samples from the full data set.
However, we cannot perform the separation in this way because
Bott's method requires data on a regular grid as well as having model elements
directly below each data point.
Thus, we take as our training set the points from the observed data grid that
fall on a similar grid but with twice the grid spacing
(open circles in Fig.~\ref{fig:grid_separation}).
All other points from the original data grid
make up the testing data set
(black dots in Fig.~\ref{fig:grid_separation}).
This separation will lead to
a testing data set with more points than the training data set.
A way to balance this loss of data in the inversion
is to generate a data grid with half of the desired grid spacing,
either through interpolation
or from a spherical harmonic model.

\subsubsection{Estimating $z_{ref}$ and $\Delta\rho$}

@@

We perform the cross-validation procedures in two parts.
First, we run the cross-validation to estimate
an optimal regularization parameter ($\mu$).
The starting estimate for all inversions is
60 km depth for all model parameters.
For this cross-validation,
we keep $z_{ref}$ and $\Delta\rho$ fixed to
$20\ km$ and $500\ kg/m^3$, respectively.
Second, we use the estimated $\mu$ to run the cross-validation
to estimate $z_{ref}$ and $\Delta\rho$,
thus obtaining the final estimated Moho depths.
Fig.~\ref{fig:crust1-results} summarizes the results
from both cross-validation runs and the final inversion results.
